\Huge{Vipassana for Hackers} \\ \large{Paper Two: The Brain} \\ \large\textit{Version 0.2}

### 2019-09-29 paper-two/paper-two.tex
2 comment correction made

The critical role of the medial temporal lobe (MTL) which is a part of the DMN 
in long term memory is well documented. \cite{mtl}
This network has also been activated during autobiographical memory retrieval, 
contextual association, and semantic knowledge. \cite{defaultnetworkadaptive}

@@

\todo{Summarize DMN? Maybe introduce why it's relevant to meditation?}
Therefore the DMN that plays a role in constructing a sense of self, in memory, 
in thinking about other also lends itself to excessive rumination and anxiety. \citr{dmndepression} 
When I sit down to meditate and my thoughts wander away (and how they wander!),
it is the DMN that is being activated.

@@

\todo{Summarize CEN? Relevance to meditation?}

>>>>

The critical role of the Medial Temporal Lobe (MTL) which is a part of the DMN 
in long term memory is well documented. \cite{mtl}
This network has also been activated during autobiographical memory retrieval, 
contextual association, and semantic knowledge. \cite{defaultnetworkadaptive}

@@

\todo{Summarize DMN? Maybe introduce why it's relevant to meditation?}
Therefore the DMN that plays a role in constructing a sense of self, in memory, 
in thinking about other also lends itself to excessive rumination and anxiety. \cite{dmndepression} 
When I sit down to meditate and my thoughts wander away (and how they wander!),
it is the DMN that is being activated.

@@

So, the Central Executive Network is involved in

cultivate their abilities to
monitor cognitive processes related to attention and distraction, making them well suited to
report on these mental events.
\todo{Summarize CEN? Relevance to meditation?}
